Make any stupid plot you want

### 2020-12-24 draft/sections/math.tex
specifying the domain of $nu$

In this section we will define the artist as a mapping from a sheaf $\mathcal{O}(E)$  to $\mathcal{O}(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}
The artist decomposes to data $E$ to visual mappings $V$ and $V$ mappings pulled back along $\xi$ to $\xi^*V$ which is then composited to a visual in prerender space $H$.

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable $\mu$ \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The space of visual variables types in $P$ is restricted to the types $Q$ takes as input.

\subsubsection{Example} 
Given a  $Q$ that manufactored lines with signature $Q(\mu_{xpos}, \mu_{ypos}, \mu_{width}, \mu_{color}, \mu_{style})$ then the $P=\Gamma(\mu)$ for this line artist would be:
\begin{itemize}
    \item $C = \{\text{xpos, ypos, width, color, style}\}$ 
    \item $DT =\{\mathbb{R}, \mathbb{R}, \mathbb{R}, \mathbb{R}^3, f:s\mapsto\mathbb{R}^3 \}$ 
    \item $P = U \times_{DT} C$
\end{itemize}

\subsubsection{Visual Channels}
The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \begin{tikzcd}
        E \arrow[d, "\pi"'] \arrow[r, "\nu"] & V \arrow[ld, "\pi"'] \\
        K                                    &                     
        \end{tikzcd}
\end{equation}

@@

>>>>

In this section we will define the artist as a mapping from a sheaf $\mathcal{O}(E)$  to $\mathcal{O}(H)$. 
\begin{equation}
    A: \mathcal{O}(E) \rightarrow \mathcal{O}(H)
\end{equation}

The artist decomposes to mapping data to visual $\nu:E\rightarrow V$, then  compositing $V$ pulled back along $\xi$ to $\xi^*V$ to a visual mark in prerender space $Q:\xi^*V\rightarrow H$.

@@

The visual fiber bundle ($V$, $K$, $\pi$, $P$) has section $\mu: V \rightarrow K$ that resolves to a visual variable \cite{bertinIIPropertiesGraphic2011,munznerMarksChannels} in fiber $P$. The visual transformer $\nu$ is a set of functions each targeting a different $\mu$
\begin{equation}
    \label{eq:nu_expanded}
    \nu:\{\nu_{0}, \ldots, \nu_{n}\} \rightarrow \{\mu_{0}, \ldots, \mu_{n}\}
\end{equation}

where $\mu_{i}$ are the visual parameters in the assembly function $Q(\mu_{0}, \ldots, \mu_{n})(s) = \rho(s)$.

\subsubsection {Example: Matplotlib Visual Fiber}
For example, for Matplotlib \cite{hunterMatplotlib2DGraphics2007}, some of the possible types in $P$ are:
\begin{table}[ht]
    \renewcommand{\arraystretch}{2}
    \begin{tabulary}{\textwidth}{|l|C|L|}\hline
     $\nu_{i}$                      & $\mu_{i}$                                                            & $dom(\nu_{i})$  \\ \hline                                              
    position                    & x, y, z                                                          & $\mathbb{R}$   \\ \hline
    size                        & linewidth, markersize                                            & $\mathbb{R}$   \\ \hline
    shape                       & markerstyle                                                      & $((\mathbb{R}, \mathbb{R}), x \in \{0,1,2,3,4,79\})^{n}^{\dag}$ \\ \hline
    color                       & color, colors, linecolor, facecolor, markerfacecolor, edgecolor  & $\mathbb{R}^4$ \\ \hline
    \multirow{2}{*}{texture}    & hatch                                                            & $/^*\backslash^*-^*+^*x^*o^*O^*.^**^* \in \Sigma^{+}$ \newline $\Sigma=\{/, \backslash, |, -, +, x, o, O, ., *\}^{\ddag}$\\\cline{2-3}
                                & linestyle                                                        & $(\mathbb{Z}, (\mathbb{Z}^n))^{\dag}$ \\ \hline              
    \end{tabulary}
    \caption{\\
        \footnotesize{\dag $n>0$}\\
        \footnotesize{\ddag$\Sigma^+=\cup_{n\in\mathbb{Z}^+}\Sigma^n$}

    }
\end{table}

\subsubsection{Visual Channels}
The function $\nu: E \rightarrow V$ is a mapping from the data bundle to the visual bundle 
\begin{equation}
    \label{eq:nu_categorical}
\begin{tikzcd}
    E_1 \arrow[r] \arrow[r, "\nu"] \arrow[d, "f"'] & V_1 \arrow[d, "f"] \\
    E_2 \arrow[r, "\nu"]                           & V_2               
\end{tikzcd}
\end{equation}

@@

+2 on data side means +2 on visual side

.2 = E1 - lambda e -> .2 V1 = .2
+.2                              +.2
.4 = E2 - lambda e -> .2 V2 = .2

.2 = E1  - lambda e-> .2 V1 = .2

                        V2 = .2

1 = E1 - lambda e->e/5 = .25

+ 1                      +.25

2 = E2 - lambda e->e/5 = .5

preserve unique mapping? does $\nu$ need to be invertable?

shifts in either space need to be mirrored in the other space, this is not valid  here's why:
$\lambda e: .2$ 
\begin{equation}
    \label{eq:nu_equation_bad}
    \begin{tikzcd}
        E_1 \arrow[r] \arrow[r, "\lambda:e\mapsto.5"] \arrow[d, "e+2"'] & V_1 \arrow[d, "h+2"] \\
        E_2 \arrow[r, "\lambda"]                                        & V_2                 
    \end{tikzcd}
\end{equation}

{x,y} = {1,2}
{y,x} = {2,1}
{y,x} = {1,2}
